TBD

### 2019-09-18 manuscript/supplementary_material.Rmd
update repo for Evolutionary Letters submission

\beginsupplement <!-- start numbering for supplementary material -->

@@

```{r LarvalPtoid Evolvability, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:LarvalPtoidEvolvability}Change in average evolvability for 10,000 random G-matrices using our best (mean) estimate of the curvature matrix for selection in the absence of egg parasitoids vs. the original food web. We found that the curvature imposed by the loss of egg parasitoids decreased evolvability in 57% of the G-matrices (i.e. the change in evolvability was negative for 57% of the simulations), which is smaller in magnitude, but in the same direction, as the effects of losing larval parasitoids."}
knitr::include_graphics("../analyses/larvalptoid_delta_evolvability.pdf")
```

>>>>

<!-- start numbering for supplementary material -->
\beginsupplement

@@

```{r LarvalPtoid Evolvability, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:LarvalPtoidEvolvability}Change in average evolvability for 10,000 random G-matrices using our best (mean) estimate of the curvature matrix for selection in the absence of egg parasitoids vs. the original food web. We found that the curvature imposed by the simulated removal of egg parasitoids decreased evolvability in 57% of the G-matrices (i.e. the change in evolvability was negative for 57% of the simulations), which is smaller in magnitude, but in the same direction, as the effects of removing larval parasitoids."}
knitr::include_graphics("../analyses/larvalptoid_delta_evolvability.pdf")
```

### 2019-09-18 manuscript/supplementary_material.tex
update repo for Evolutionary Letters submission

\begin{figure}
\centering
\includegraphics{../analyses/larvalptoid_delta_evolvability.pdf}
\caption{\label{fig:LarvalPtoidEvolvability}Change in average
evolvability for 10,000 random G-matrices using our best (mean) estimate
of the curvature matrix for selection in the absence of egg parasitoids
vs.~the original food web. We found that the curvature imposed by the
loss of egg parasitoids decreased evolvability in 57\% of the G-matrices
(i.e.~the change in evolvability was negative for 57\% of the
simulations), which is smaller in magnitude, but in the same direction,
as the effects of losing larval parasitoids.}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics{../analyses/larvalptoid_delta_evolvability.pdf}
\caption{\label{fig:LarvalPtoidEvolvability}Change in average
evolvability for 10,000 random G-matrices using our best (mean) estimate
of the curvature matrix for selection in the absence of egg parasitoids
vs.~the original food web. We found that the curvature imposed by the
simulated removal of egg parasitoids decreased evolvability in 57\% of
the G-matrices (i.e.~the change in evolvability was negative for 57\% of
the simulations), which is smaller in magnitude, but in the same
direction, as the effects of removing larval parasitoids.}
\end{figure}
